Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-15 tab-hmeff.tex
tex

\begin{table*}
\resizebox{\linewidth}{!}{
	\setlength{\tabcolsep}{0.2em}
\begin{tabular}{cccc|cccc|ccccc|ccccc|c}
\hline 
\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Model}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Loss}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18} 
 &  &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
\hline 
\hline 
CUB & RN18 & Triplet & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline 
 &  &  & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
 &  &  & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 &  &  & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
 &  &  & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
 &  &  & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline 
 &  &  & HM:R$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline 
 &  &  & HM:S$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\end{tabular}
}

>>>>

\begin{table*}
\resizebox{\linewidth}{!}{
	\setlength{\tabcolsep}{0.2em}

\begin{tabular}{cc|cccc|ccccc|ccccc|c}
\hline 
\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{3-16} \cline{4-16} \cline{5-16} \cline{6-16} \cline{7-16} \cline{8-16} \cline{9-16} \cline{10-16} \cline{11-16} \cline{12-16} \cline{13-16} \cline{14-16} \cline{15-16} \cline{16-16} 
 &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
\hline 
\hline 
CUB & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline 
 & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
 & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
 & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
v7 & ACT ($\eta=16$) & R:V &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline 
 & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=2$) & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
 & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=4$) & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
 & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=8$) & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
 & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=16$) & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
 & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=32$) & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
\hline 
 & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=2$) & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
 & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=4$) & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
 & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=8$) & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
 & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=16$) & 36.0 & 46.2 & 20.6 & 48.5 & 14.5 & 39.7 & 15.8 & 32.8 & 0.587 & 0.678 & 18.6 & 16.8 & 27.6 & 3.1 & 36.2\tabularnewline
 & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=32$) & Q &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\end{tabular}

}
